Multiresolution Neural Field Estimation

### 2011-03-01 Multiresolution_framework/ltx/manuscript.tex
edits to results

The spatial frequency of the observed field is shown in \figurename{\ref{fig:KernelAndFreqResponse}} (b), showing a spatially band-limited signal. This suggests the use of wavelets up to level $j=2$ (with the bandwidth $\approx[2.5,4]$ cycles/mm) can fully represent the field. Note that wavelets due to their bandpass filter characteristics extract successively higher and higher frequency components by increasing $j$.

>>>>

\cut{The spatial frequency of the observed field is shown in \figurename{\ref{fig:KernelAndFreqResponse}} (b), showing a spatially band-limited signal. This suggests the use of wavelets up to level $j=2$ (with the bandwidth $\approx[2.5,4]$ cycles/mm) can fully represent the field. Note that wavelets due to their bandpass filter characteristics extract successively higher and higher frequency components by increasing $j$.}
